%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Wolfram Research, Inc.} % Organization
    {Champaign, IL} % Location
    {Apr 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed/Implemented various configuration management and remote execution frameworks such as Salt and Puppet for the various Wolfram Cloud environments.}
        \item {Personally architected software platforms, individual servers, machine clusters, and deployment workflows.}
        \item {Provided routine performance and security analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Systems Administrator} % Job title
    {Wolfram Research, Inc.} % Organization
    {Champaign, IL} % Location
    {Dec 2016 - Apr 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided general systems administration for various Wolfram web products and services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Systems Intern} % Job title
    {Wolfram Research, Inc.} % Organization
    {Champaign, IL} % Location
    {Sep 2016 - Dec 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a myriad of development projects pertaining to custom Docker images and the Wolfram Engine kernel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mathematics and Technology Tutor} % Job title
    {Tallahassee Community College} % Organization
    {Tallahassee, FL} % Location
    {May 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided tutoring and support to students in various mathematics and technology topics.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
